Bow shocks, bow waves, and dust waves. IV. Shell shape statistics

### 2019-07-10 papers/Papers1234/sigma-ori-arcs.tex
Add N-T distro figure and write caption

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{figs/sigma-ori-N-T-histogram}
  \caption{Joint distribution of dust temperature and gas column
    density. Gray-scale image shows the fraction of the emission at
    \SI{160}{\um} (cool component, upper-left) and \SI{24}{\um} (warm
    component, lower right) that is contributed by pixels with a given
    \((T, N)\) combination. Conversion from dust optical depth to
    hydrogen column density is carried out using the empirical
    calibration described in the text.}
  \label{fig:N-T-distro}
\end{figure}
